Changing Flights In The Air\\ (Abortable Chain Agreement)

### 2015-05-09 paper/abstract2.tex
Work on the abstract

    The key novelty of our framework is its practial applicability, having state
    of the art optimization techniques built-in: it supports executing commutative commands 
    without synchronization, optimizing the execution of read-only commands,
    minimizing the size of crucial data structures.

    We present a detailed, mechanically-proved formalization of our framework
    and we show how several SMR algorithms fit into our framework.
    We classify SMR algorithms in two categories corresponding to two abstract
    specifications that the algorithms refine.

>>>>

    The key novelty of our framework is its practical applicability, having state
    of the art optimization and reconfiguration techniques built-in: tolerating k fault with k+1
    replicas using an external reconfiguration master, executing commutative commands 
    without synchronization, optimizing the execution of read-only commands,
    minimizing the size of crucial data structures.

    Moreover, our framework allows a novel characterization of SMR algorithms in two categories corresponding to two abstract
    specifications that the algorithms refine. The two categories represent a
    fundamental three-dimensional trade-off relating resilience to crashes,
    resilience to contention, and processing latency. Cluster idea?

    We present a detailed, mechanically-proved formalization of our framework in
    Isabelle/HOL, and we show how several SMR algorithms fit into our framework.
